% REQUIRED PACKAGES    -------------------------------------------------------------------------
%
% +++
%
% Install with: sudo apt install ...
% texlive-latex-base
% texlive-latex-recommended
% texlive-latex-extra
% texlive-fonts-recommended
% texlive-fonts-extra
% cm-super
%
% +++
%
% Install other missing packages using: tlmgr install pdflatex
%
% +++
%
% Render document: cd tex; pdflatex CV-Michael-Jahn-short.tex
%
%%  FORMAT     ---------------------------------------------------------------------------------
\documentclass[10pt, a4paper, sans]{moderncv}
\moderncvcolor{green} % 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' 'red'
\moderncvstyle{casual} % 'casual', 'classic', 'oldstyle', 'banking'
\RequirePackage[sfdefault,light]{roboto}

%%  INFO       ---------------------------------------------------------------------------------
\firstname{Michael}
\familyname{Jahn}
\title{Curriculum vitae}
% \email{jahn$@$email.de}
% \photo[0.15\textwidth]{../figures/profile_2020.png}


\begin{document}

\newpage

\maketitle

\setcounter{page}{1}


\section{Personal information}
\cvitem{Name}{Dr. rer. nat. Michael Jahn}
\cvitem{Date of birth}{Dec 31, 1985, in Dresden, Germany}
\cvitem{Email}{jahn@mpusp.mpg.de}


\section{Current position}
\cventry{8/2022--now}{Staff scientist}{}{Bioinformatics Platform, Laboratory of Emmanuelle Charpentier, Max-Planck-Unit for the Science of Pathogens (MPUSP), Berlin}{}{}


\section{Work}
\cventry{5/2016--5/2022}{Postdoctoral scientist}{}{System-wide analysis and metabolic engineering of autotrophic bacteria in the group of Prof Paul Hudson, Science For Life Laboratory - Royal Institute of Technology, Stockholm}{}{}
\cventry{8--12/2009}{Erasmus internship}{}{Center of Excellence in Evolutionary Genetics and Physiology at the group of Prof Mikko Nikinmaa, Dept. of Biology, University of Turku, Finland}{}{}


\section{Education}
\cventry{2011--2015}{PhD studies}{}{Group of Prof Susann Müller, Dept. Environmental Microbiology, Helmholtz-Centre for Environmental Research, Leipzig}{}{}
\cventry{2005--2011}{Diploma studies, biology}{}{Dresden University of Technology (TUD), main subjects: genetics, biochemistry, immunology}{}{}


\section{Roles and Qualifications}
\cvitem{Roles}{Approved project manager for genetic works (\S ~14,15 GenTSV), 2015-2025.}
\cvitem{}{Data protection officer, from 2025.}
\cvitem{}{Active peer reviewer for Microbial Cell Factories, Frontiers, PLOS Comp Bio, etc.}
\cvitem{}{Member of the \link[Snakemake]{https://github.com/snakemake} organization, contributor and co-author.}
\cvitem{Programming}{Fluent in Python, R, Snakemake, Linux bash, Markdown, Latex, Git}
\cvitem{Software}{
	\link[WeightedTreemaps]{https://github.com/m-jahn/WeightedTreemaps},
	\link[ShinyProt]{https://m-jahn.shinyapps.io/ShinyProt/},
	\link[ShinyLib]{https://m-jahn.shinyapps.io/ShinyLib/},
	\link[fluctuator]{https://github.com/m-jahn/fluctuator}
	\link[snakemake-workflow-catalog]{https://github.com/snakemake/snakemake-workflow-catalog},
	\link[snakemake-crispr-guides]{https://github.com/mpusp/snakemake-crispr-guides},
	\link[snakemake-simple-mapping]{https://github.com/mpusp/snakemake-simple-mapping},
	\link[snakemake-workflow-template]{https://github.com/mpusp/snakemake-workflow-template},
	\link[nf-core-crispriscreen]{https://github.com/MPUSP/nf-core-crispriscreen}
}
\cvitem{Languages}{Fluent in German, English and Swedish}


\section{Top 5 Publications}

\cvitem{\listitemsymbol}{\textbf{Jahn M} et al., \textit{The energy metabolism of Cupriavidus necator in different trophic conditions}. Applied and Environmental Microbiology, \textbf{2024}.
\link[Link]{https://doi.org/10.1128/aem.00748-24}.}

\cvitem{\listitemsymbol}{\underline{Miao R, \textbf{Jahn M}} et al., \textit{CRISPR interference screens reveal growth–robustness tradeoffs in Synechocystis sp. PCC 6803 across growth conditions}. The Plant Cell, \textbf{2023}.
\link[Link]{https://doi.org/10.1093/plcell/koad208}.}

\cvitem{\listitemsymbol}{\textbf{Jahn M} et al., \textit{Protein allocation and utilization in the versatile chemolithoautotroph Cupriavidus necator}, eLife, 10, \textbf{2021}.
\link[Link]{https://elifesciences.org/articles/69019}.}

\cvitem{\listitemsymbol}{Yao L et al., \textbf{Jahn M}, Hudson EP. \textit{Pooled CRISPRi screening of the cyanobacterium Synechocystis sp PCC 6803 for enhanced industrial phenotypes}. Nature Communications, \textbf{2020}.
\link[Link]{https://www.nature.com/articles/s41467-020-15491-7}.}

\cvitem{\listitemsymbol}{\textbf{Jahn M} et al., \textit{Growth of Cyanobacteria Is Constrained by the Abundance of Light and Carbon Assimilation Proteins}. Cell Reports 25, 478–486.e8., \textbf{2018}.
\link[Link]{https://linkinghub.elsevier.com/retrieve/pii/S2211124718314852}.}

\end{document}
